Tropical Andes plant trait data BIEN

### 2023-07-31 code/L0/L0_TropicalAndes_plants_TRY_traits.Rmd
add code to summarize trait count correct spelling error (thanks cats)

# Load required packages
```{r}
library(rtry)
```

# Load TRY data
Data was obtained from https://www.try-db.org/TryWeb/Prop0.php 
```{r}
try_data <- rtry_importujkgh("G:/Shared drives/SpaCE_Lab_FRUGIVORIA/data/plants/L0/TRY/25496_17032023010024/25496.txt")
```

@@

>>>>

# Load required packages
```{r}
library(rtry)
library(dplyr)
```

# Load TRY data
Data was obtained from https://www.try-db.org/TryWeb/Prop0.php 
```{r}
try_data <- rtry_import("G:/Shared drives/SpaCE_Lab_FRUGIVORIA/data/plants/L0/TRY/25496_17032023010024/25496.txt")
```

@@

```{r}
try_data_TropicalAndes %>% count(TraitName)
```
